### 2023-11-21 paper/content.tex
Updates from Overleaf

To recover magnetic direction and moment we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetization is uniform.
This last premise aligns with the theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable sensor-sample height, which is the basis of classical paleomagnetism.
Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
Therefore, this method can be quickly replicated in a data set of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.

>>>>

To recover magnetic direction and moment we only need to assume that for each data window there is one source with it's central positions known (so we apply Euler deconvolution) and the magnetization is uniform.
This last premise aligns with the theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable sensor-sample height, which is the basis of classical paleomagnetism.
Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
Therefore, this method can be quickly replicated in a data set of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.
